Visualization

### 2022-12-08 Code/UpdatedBlockBootstrap.Rmd
Repo Update

  ## two intervals  
  nm = quantile(bt$nm.stat, probs = c(0.025, 0.975))
  mv = quantile(bt$mv.stat, probs = c(0.025, 0.975))

  nm.cov <- nm[1] < target && target < nm[2]
  mv.cov <- mv[1] < target && target < mv[2]

@@

  ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
  c(nm.cov, mv.cov)
}

@@

```{r more_functions, echo = False}
options(max.print = 1000000)
#ar1 <- function(x) cor(x[-1], x[-length(x)])
ar1 <- function(x) acf(x, plot = FALSE, lag.max = 1)$acf[2]
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, rm[1] - qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000), rm[1] + qnorm(.975) * sqrt((rm[1] * (1 - rm[1])) / 4000),  rm[2] - qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000), rm[2] + qnorm(.975) * sqrt((rm[2] * (1 - rm[2])) / 4000))
}

@@

```{r Normal Sample n = 32}
set.seed(1)
(m_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_norm_32 = c(32, my_summary(replicate(4000, do1rep(32, 0, 0.1, 0, ceiling(32**(1/3)), ar1)))))
```

```{r Normal Sample n = 64}
set.seed(5)
(m_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_norm_64 = c(64, my_summary(replicate(4000, do1rep(64, 0, 0.1, 0, ceiling(64**(1/3)), ar1)))))
```

```{r Normal Sample n = 128}
set.seed(10)
(m_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_norm_128 = c(128, my_summary(replicate(4000, do1rep(128, 0, 0.1, 0, ceiling(128**(1/3)), ar1)))))
```

```{r Normal Sample n = 256}
set.seed(50)
(m_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_norm_256 = c(256, my_summary(replicate(4000, do1rep(256, 0, 0.1, 0, ceiling(256**(1/3)), ar1)))))
```

```{r Normal Sample n = 512}
set.seed(100)
(m_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_norm_512 = c(512, my_summary(replicate(4000, do1rep(512, 0, 0.1, 0, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 32}
set.seed(1)
(m_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_0.2_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.2, 0.1, 0.2, ceiling(32**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 64}
set.seed(5)
(m_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_0.2_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.2, 0.1, 0.2, ceiling(64**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 128}
set.seed(10)
(m_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_0.2_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.2, 0.1, 0.2, ceiling(128**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 256}
set.seed(50)
(m_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_0.2_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.2, 0.1, 0.2, ceiling(256**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 512}
set.seed(100)
(m_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_0.2_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.2, 0.1, 0.2, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 1024}
set.seed(500)
(m_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0, ceiling(1024**(1/3)), m1)))))
set.seed(500)
(ar_0.2_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.2, 0.1, 0.2, ceiling(1024**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 2048}
set.seed(1000)
(m_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0, ceiling(2048**(1/3)), m1)))))
set.seed(1000)
(ar_0.2_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.2, 0.1, 0.2, ceiling(2048**(1/3)), ar1)))))
```

```{r AR = 0.2 Sample n = 4096}
set.seed(5000)
(m_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0, ceiling(4096**(1/3)), m1)))))
set.seed(5000)
(ar_0.2_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.2, 0.1, 0.2, ceiling(4096**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 32}
set.seed(1)
(m_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0, ceiling(32**(1/3)), m1)))))
set.seed(1)
(ar_0.4_32 = c(32, my_summary(replicate(4000, do1rep(32, 0.4, 0.1, 0.4, ceiling(32**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 64}
set.seed(5)
(m_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0, ceiling(64**(1/3)), m1)))))
set.seed(5)
(ar_0.4_64 = c(64, my_summary(replicate(4000, do1rep(64, 0.4, 0.1, 0.4, ceiling(64**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 128}
set.seed(10)
(m_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0, ceiling(128**(1/3)), m1)))))
set.seed(10)
(ar_0.4_128 = c(128, my_summary(replicate(4000, do1rep(128, 0.4, 0.1, 0.4, ceiling(128**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 256}
set.seed(50)
(m_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0, ceiling(256**(1/3)), m1)))))
set.seed(50)
(ar_0.4_256 = c(256, my_summary(replicate(4000, do1rep(256, 0.4, 0.1, 0.4, ceiling(256**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 512}
set.seed(100)
(m_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0, ceiling(512**(1/3)), m1)))))
set.seed(100)
(ar_0.4_512 = c(512, my_summary(replicate(4000, do1rep(512, 0.4, 0.1, 0.4, ceiling(512**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 1024}
set.seed(500)
(m_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0, ceiling(1024**(1/3)), m1)))))
set.seed(500)
(ar_0.4_1024 = c(1024, my_summary(replicate(4000, do1rep(1024, 0.4, 0.1, 0.4, ceiling(1024**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 2048}
set.seed(1000)
(m_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0, ceiling(2048**(1/3)), m1)))))
set.seed(1000)
(ar_0.4_2048 = c(2048, my_summary(replicate(4000, do1rep(2048, 0.4, 0.1, 0.4, ceiling(2048**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 4096}
set.seed(5000)
(m_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0, ceiling(4096**(1/3)), m1)))))
set.seed(5000)
(ar_0.4_4096 = c(4096, my_summary(replicate(4000, do1rep(4096, 0.4, 0.1, 0.4, ceiling(4096**(1/3)), ar1)))))
```

```{r AR = 0.4 Sample n = 8192}
set.seed(10000)
(m_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0, ceiling(8192**(1/3)), m1)))))
set.seed(10000)
(ar_0.4_8192 = c(8192, my_summary(replicate(4000, do1rep(8192, 0.4, 0.1, 0.4, ceiling(8192**(1/3)), ar1)))))
```

```{r}
m_0 <- data.frame(rbind(m_norm_32, m_norm_64, m_norm_128, m_norm_256, m_norm_512))
ar_0 <- data.frame(rbind(ar_norm_32, ar_norm_64, ar_norm_128, ar_norm_256, ar_norm_512))
m_0.2 <- data.frame(rbind(m_0.2_32, m_0.2_64, m_0.2_128, m_0.2_256, m_0.2_512, m_0.2_1024, m_0.2_2048, m_0.2_4096))
ar_0.2 <- data.frame(rbind(ar_0.2_32, ar_0.2_64, ar_0.2_128, ar_0.2_256, ar_0.2_512, ar_0.2_1024, ar_0.2_2048, ar_0.2_4096))
m_0.4 <- data.frame(rbind(m_0.4_32, m_0.4_64, m_0.4_128, m_0.4_256, m_0.4_512, m_0.4_1024, m_0.4_2048, m_0.4_4096, m_0.4_8192))
ar_0.4 <- data.frame(rbind(ar_0.4_32, ar_0.4_64, ar_0.4_128, ar_0.4_256, ar_0.4_512, ar_0.4_1024, ar_0.4_2048, ar_0.4_4096, ar_0.4_8192))
colnames(m_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(m_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0.2) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(m_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
colnames(ar_0.4) <- c('Sample Length', 'Non-Moving Coverage Rate', 'Moving Coverage Rate', 'Non-Moving Lower Bound', 'Non-Moving Upper Bound', 'Moving Lower Bound', 'Moving Upper Bound')
m_0
ar_0
m_0.2
ar_0.2
m_0.4
ar_0.4
write.csv(m_0,"../Data/m_0.csv", row.names = FALSE)
write.csv(ar_0,"../Data/ar_0.csv", row.names = FALSE)
write.csv(m_0.2,"../Data/m_0.2.csv", row.names = FALSE)
write.csv(ar_0.2,"../Data/ar_0.2.csv", row.names = FALSE)
write.csv(m_0.4,"../Data/m_0.4.csv", row.names = FALSE)
write.csv(ar_0.4,"../Data/ar_0.4.csv", row.names = FALSE)
```

>>>>

  ## two intervals for each statistic
  ret <- c()
  num <- dim(bt$nm.stat)[1]
  for (s in 1:num) {
    nm = quantile(bt$nm.stat[s,], probs = c(0.025, 0.975))
    ret <- append(ret, nm[1] < target[s] && target[s] < nm[2])
    mv = quantile(bt$mv.stat[s,], probs = c(0.025, 0.975))
    ret <- append(ret, mv[1] < target[s] && target[s] < mv[2])
  }

@@

  ## returns statistics and standard error's for nm and mv respectively, standard error (sd(bt$mv.stat) is estimated as the sqrt(sample_variance(X_t) / n)
  #c(nm.cov, mv.cov)
  c(ret)
}

@@

```{r more_functions, echo = False}
options(max.print = 1000000)
#ar1 <- function(x) cor(x[-1], x[-length(x)])
ar1 <- function(x) c(acf(x, plot = FALSE, lag.max = 1)$acf)[2]
m1 <- function(x) mean(x)
s1 <- function(x) c(mean(x), acf(x, plot = FALSE, lag.max = 1)$acf[2], var(x))

my_summary <- function(x, alpha = .05)
{
  n = dim(x)[2]
  ret <- c()
  rm = rowMeans(x)
  for (s in rm) {
    ret = append(ret, c(s, s - qnorm(1 - alpha/2) * sqrt((s * (1 - s)) / n), s + qnorm(1 - alpha/2) * sqrt((s * (1 - s)) / n)))
  }
  c(ret)
}

@@

```{r Theta = 0, Sigma = 0.1, n = 32}
my.summary <- data.frame(matrix(ncol = 21, nrow = 0))
colnames(my.summary) <- c('theta', 'sigma', 'n', 'nm.cov.mu', 'nm.lower.mu', 'nm.upper.mu', 'mv.cov.mu', 'mv.lower.mu', 'mv.upper.mu', 'nm.cov.theta', 'nm.lower.theta', 'nm.upper.theta', 'mv.cov.theta', 'mv.lower.theta', 'mv.upper.theta', 'nm.cov.sigsq', 'nm.lower.sigsq', 'nm.upper.sigsq', 'mv.cov.sigsq', 'mv.lower.sigsq', 'mv.upper.sigsq')
nrep <- 4000
statistic <- s1
mu <- 0
theta <- 0
sigma <- 0.1
set.seed(1)
n <- 32
d_0_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_32)))
```

```{r Theta = 0, Sigma = 0.1, n = 64}
set.seed(5)
n <- 64
d_0_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_64)))
```

```{r Theta = 0, Sigma = 0.1, n = 128}
set.seed(25)
n <- 128
d_0_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_128)))
```

```{r Theta = 0, Sigma = 0.1, n = 256}
set.seed(125)
n <- 256
d_0_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_256)))
```

```{r Theta = 0, Sigma = 0.1, n = 512}
set.seed(625)
n <- 512
d_0_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_512)))
```

```{r Theta = 0, Sigma = 0.1, n = 1024}
set.seed(3125)
n <- 1024
d_0_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.1_1024)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 32}
theta <- 0.2
set.seed(3)
n <- 32
d_0.2_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_32)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 64}
set.seed(15)
n <- 64
d_0.2_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_64)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 128}
set.seed(75)
n <- 128
d_0.2_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_128)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 256}
set.seed(375)
n <- 256
d_0.2_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_256)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 512}
set.seed(1875)
n <- 512
d_0.2_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_512)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 1024}
set.seed(9375)
n <- 1024
d_0.2_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_1024)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 2048}
set.seed(46875)
n <- 2048
d_0.2_0.1_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_2048)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 4096}
set.seed(234375)
n <- 4096
d_0.2_0.1_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_4096)))
```

```{r Theta = 0.2, Sigma = 0.1, n = 8192}
set.seed(1171875)
n <- 8192
d_0.2_0.1_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.1_8192)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 32}
theta <- 0.4
set.seed(5)
n <- 32
d_0.4_0.1_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_32)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 64}
set.seed(25)
n <- 64
d_0.4_0.1_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_64)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 128}
set.seed(125)
n <- 128
d_0.4_0.1_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_128)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 256}
set.seed(625)
n <- 256
d_0.4_0.1_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_256)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 512}
set.seed(3125)
n <- 512
d_0.4_0.1_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_512)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 1024}
set.seed(15625)
n <- 1024
d_0.4_0.1_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_1024)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 2048}
set.seed(78125)
n <- 2048
d_0.4_0.1_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_2048)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 4096}
set.seed(390625)
n <- 4096
d_0.4_0.1_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_4096)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 8192}
set.seed(1953125)
n <- 8192
d_0.4_0.1_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_8192)))
```

```{r Theta = 0.4, Sigma = 0.1, n = 16384}
set.seed(9765625)
n <- 16384
d_0.4_0.1_16384 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.1_16384)))
```

```{r Theta = 0, Sigma = 0.5, n = 32}
theta <- 0
sigma <- 0.5
set.seed(1)
n <- 32
d_0_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_32)))
```

```{r Theta = 0, Sigma = 0.5, n = 64}
set.seed(5)
n <- 64
d_0_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_64)))
```

```{r Theta = 0, Sigma = 0.5, n = 128}
set.seed(25)
n <- 128
d_0_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_128)))
```

```{r Theta = 0, Sigma = 0.5, n = 256}
set.seed(125)
n <- 256
d_0_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_256)))
```

```{r Theta = 0, Sigma = 0.5, n = 512}
set.seed(625)
n <- 512
d_0_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_512)))
```

```{r Theta = 0, Sigma = 0.5, n = 1024}
set.seed(3125)
n <- 1024
d_0_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0_0.5_1024)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 32}
theta <- 0.2
set.seed(3)
n <- 32
d_0.2_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_32)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 64}
set.seed(15)
n <- 64
d_0.2_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_64)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 128}
set.seed(75)
n <- 128
d_0.2_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_128)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 256}
set.seed(375)
n <- 256
d_0.2_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_256)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 512}
set.seed(1875)
n <- 512
d_0.2_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_512)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 1024}
set.seed(9375)
n <- 1024
d_0.2_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_1024)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 2048}
set.seed(46875)
n <- 2048
d_0.2_0.5_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_2048)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 4096}
set.seed(234375)
n <- 4096
d_0.2_0.5_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_4096)))
```

```{r Theta = 0.2, Sigma = 0.5, n = 8192}
set.seed(1171875)
n <- 8192
d_0.2_0.5_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.2_0.5_8192)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 32}
theta <- 0.4
set.seed(5)
n <- 32
d_0.4_0.5_32 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_32)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 64}
set.seed(25)
n <- 64
d_0.4_0.5_64 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_64)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 128}
set.seed(125)
n <- 128
d_0.4_0.5_128 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_128)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 256}
set.seed(625)
n <- 256
d_0.4_0.5_256 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_256)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 512}
set.seed(3125)
n <- 512
d_0.4_0.5_512 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_512)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 1024}
set.seed(15625)
n <- 1024
d_0.4_0.5_1024 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_1024)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 2048}
set.seed(78125)
n <- 2048
d_0.4_0.5_2048 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_2048)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 4096}
set.seed(390625)
n <- 4096
d_0.4_0.5_4096 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_4096)))
```

```{r Theta = 0.4, Sigma = 0.5, n = 8192}
set.seed(1953125)
n <- 8192
d_0.4_0.5_8192 <- replicate(nrep, do1rep(n, theta, sigma, c(mu, theta, sigma^2), ceiling(n**(1/3)), statistic))
(my.summary[nrow(my.summary) + 1,] <- c(theta, sigma, n, my_summary(d_0.4_0.5_8192)))
```

```{r}
my.summary
```

```{r}
library(tidyr)
(summary.df <- my.summary %>%
  pivot_longer(
    cols = nm.cov.mu:mv.upper.sigsq,
    names_to = c('method', '.value', 'target'),
    names_pattern = "(.*)\\.(.*)\\.(.*)"
  ))
write.csv(summary.df,"../Data/summary.df.csv", row.names = FALSE)
```

```{r}
write.csv(my.summary,"../Data/my.summary.csv", row.names = FALSE)
```
